The low dimensional world of echolocating bats

### 2020-03-25 Paper/main.tex
filled all the xxs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%number of pca components
\newcommand{\pca}{xx}
%number of neurons in models
\newcommand{\nneurons}{xx}
%number of connections
\newcommand{\nweights}{37 thousand}

@@

Echolocating bats are long-lived, mobile animals. They use the landscape intensively for foraging, roosting, and commuting. They have excellent spatial memory \citep{Barchi2013,VonHelversen2005} and can rely on sonar to navigate to notable locations like foraging grounds, drinking places \citep[see][for references]{Vanderelst2016,Vanderelst2017}. Furthermore, bats have been reported to use sonar-based recognition of landmarks, both under experimental \citep{Jensen2005,Yu2019}, and natural \citep{Verboom1999} conditions. Echolocating bats can navigate to salient places \citep{Schnitzler2003}, relying solely on their sonar system. Indeed, bats deprived of sight have been found to successfully return to their roost when displaced by up to 40 miles \citep{Stones1969,Williams1966,Davis1970,Mueller1957}.

@@

However, it should be noted that such low dimensional descriptions have been shown to potentially contain a lot of useful information \citep{Kuc1997b,Kuc1997}. We previously demonstrated that bats might use sonar template-based scene recognition \citep{Vanderelst2016,Vanderelst2017}. In this approach, bats are assumed to compare the acoustic signature of the environment to a set of previously stored signatures. We operationalized these acoustic signatures as time-intensity profiles, which could be derived directly from the cochlear output.

In this paper, we directly evaluate the hypothesis that sonar provides bats inherently with a low dimensional, yet functionally sufficient, description of the world. We test this hypothesis in two steps. In a first step, we generate an extensive collection of synthetic echo sequences. Next, we process the echo sequences using a model of the bat's auditory periphery \citep{Wiegrebe2008}. We assess the compressibility of the output of the cochlear model using \PCA. The synthetic echo sequences differ greatly in complexity. Nevertheless, the output of the cochlear model can be mapped onto a low-dimensional space. In a second step, we show that echoes collected in real bat habitats can be mapped into the same low-dimensional space, without loss of information. We verify this by demonstrating that the low dimensional feature space allows recognizing locations in real habitats.

@@

We created artificial echo sequences by randomly spacing ideal point reflectors. The distances of the point reflectors were selected using a two-step process. First we selected $n_{s}$ seed points $s$, uniformly distributed over a range from 0.5 to 7 meters. Next, for every seed point $s$, we selected $n_{c}$ cloud points normally distributed around $s$, with standard deviation 0.25 m. We added a single reflector at a distance between xx and xx to each collection of points. This two step process to modeling natural reflectors was inspired by the results of \citet{Yovel2009}, who found that echoes returning from vegetation could be better modeled using a similar two-step process than simply using uniformly spaced points. We generated xx sets of points for each combination of $n_s \in [xx,xx,xx, xx]$ and $n_c \in [xx, xx, xx, xx]$. Synthetic echoes consisting of few reflectors are likely to consist of only weak echoes.

@@

Artificial echo sequences were filtered using a model of the bat's auditory periphery, as proposed by \citet{Wiegrebe2008}. This model simulates the temporal and spectral resolution of the bat's cochlea. The model consists of a gammatone filterbank followed by half-wave rectification and non-linear compression with an exponent of 0.4. Finally, the model includes a 1 kHz low-pass filter modeling the response characteristics of the inner hair cells. In the current implementation, we used a gammatone filterbank with xx filters, centered around xx kHz. The filters were spaced to correspond to equivalent rectangular bandwidths \citep{Glasberg1990}. The output of each channel was attenuated with a time (distance) weighted factor corresponding to the atmospheric attenuation at the channel's center frequency. This operation approximated frequency-dependent atmospheric attenuation. The first 6 ms of data were removed. This was done to ensure the data corresponded with the measurement data. As indicated below, we removed the first 6 ms of the measurement  data to avoid including the pickup of the emitted signal.

Figure \ref{fig:processing} depicts a single example of a synthetic echo sequence. It also illustrates the resulting response for each of the xx channels of the \citet{Wiegrebe2008} model. From these responses, it can be seen that they are highly correlated across channels. This is confirmed when analyzing the average cross-channel correlation for all xx synthetic echo sequences (Fig. \ref{fig:processing}xx). We calculated the correlation $\bar{\rho}$ between the output $X_i$ of each frequency channel $i$ and the mean across channels $\bar{X}$ for each synthetic echo, as follows,
%
\begin{equation}
\bar{\rho} = \frac{1}{n} \sum_i \frac{\mbox{cov}(X_i,\bar{X})}{\sigma_{X_i}, \sigma_{\bar{X}}} 
\end{equation}
%
The distribution of $\bar{\rho}$ is plotted in \ref{fig:processing}xx. From this distribution, it can be seen that the value of $\bar{\rho}$ ranged from xx to xx. From these high cross-channel correlations, we conclude that the output of the cochlear model can be summarized by averaging across channels without extensive loss of information.

An example of such a cross-channel sum is plotted in figure \ref{fig:processing}xx. In correspondence to our previous work \citep{Vanderelst2016}, we refer to this average across frequency channels as a template.

\begin{figure*}[tb]
	\centering
	\includegraphics[width=1\linewidth]{../results/processing}
	\caption{Example of synthetic echo sequence and its processing using the \citet{Wiegrebe2008} model. (xx) Example of a single synthetic echo sequence (red). The dechirped version is plotted in black. (xx-xx) Response of the xx frequency channels in the \citet{Wiegrebe2008} model. From these plots, it can be seen that channels correlate highly. This is confirmed in panel xx, depicting the average correlation across channels for all xx synthetic echo sequences analyzed. Note that the x-scale does not start at zero. (xx) The output of the \citet{Wiegrebe2008} model summed across the frequency channels, is referred to as a template in this paper. The template resulting from the echo sequence in panel xx is shown in panel xx. Panel xx shows the cumulative proportion of explained variance as a function of number of \pc\ across all templates for all synthetic echo sequences.}
	\label{fig:processing}
\end{figure*}

We used principal components analysis (\PCA\ ) to assess the dimensionality of the templates generated from the synthetic echo sequences. We found that almost all of the variance ($> 99\%$) in the templates could be captured by \pca\ components (see figure \ref{fig:processing}xx). Some examples of templates reconstructed from the principal components are shown in figure \ref{fig:synthetictemplates}xx).

\begin{figure*}[tb]
	\centering
	\includegraphics[width=1\linewidth]{../results/synthetic_templates}
	\caption{Example of synthetic dechirped echo sequences, their corresponding templates and the templates reconstructed from the \pca\ \pcs. (xx-xx) Three examples of synthetic echo sequence waveforms. Panels xx-xx depict the resulting templates (i.e., summation across the output channels of the \citet{Wiegrebe2008} model). These panels also show the result of projecting the templates into a \pca D \pc\ space and transforming the result back to the original coordinates.}
	\label{fig:synthetictemplates}
\end{figure*}

In this section, we  used a generative model for naturalistic echoes. We assumed that echoes sequences received by bats can be considered as generated by anisotropically distributed point reflectors. Using this model, we have derived a low dimensional space ($D = \pca$), which can be used to describe the templates resulting from the artificial echo sequences. This implies that, after filtering through (a model of) the bat's auditory system, these artificial echoes can be converted into low dimensional descriptions. The original echo sequences, generated by xx to xx point reflectors effectively map to \pca\ dimensional vector. In the remainder of the paper, we will assess whether this low dimensional space allows describing the echoes from real bat habitats as collected using an ensonification device.

@@

We should point out that we did not take any steps to avoid so-called overfitting by the neural networks. Overfitting occurs when a neural network \citep{Ghotra2017}, or other mathematical models \citep{Hawkins2004}, extract complicated relationships between inputs and outputs that do not hold beyond the training examples. Overfitting typically reduces the ability of the model to generalize its predictive power to new data. However, in this case, the model is not required to generalize to other environments. Instead, we are only interested in whether the neural networks can learn and classify the set of training examples. Nevertheless, it would be beneficial if the neural networks would be capable of classifying templates corresponding to directions that are slightly different than those included in the data sets. Indeed, this is a feature of the Euclidean distance measure used in implementing the perfect memory. In that approach, novel templates will be classified to positions with similar templates. We verified whether this properties was also found in the neural networks the case by generating a set of templates by interpolating in azimuth and elevation between the directions ensonified in the data set. In our data sets, we ensonified 31 different azimuth directions and 7 elevation directions. The interpolated data consisted of 30 azimuths and 7 elevations. We used the neural networks trained on the original data to classify these interpolated data. It was found that the neural network indeed classified these interpolated data to azimuths and elevations close to the positions from which they were interpolated (Figure \ref{fig:interpolation}).

@@

We found that the templates derived from acoustic data collected in real habitats could be well represented by the \pca\ components derived from synthetic data. This \pca-dimensional space could represent xx\% of the variance in the templates. Figure \ref{fig:empiricaltemplates} shows examples of templates and their reconstructed counterparts. Therefore, although the model used to generate echo sequences was very simple, these results indicate that the \pca D feature space derived from the generative echo model could adequately represent templates resulting from real acoustic data.

@@

Figure \ref{fig:history} depicts the training history of all networks. This figure shows that, in all cases, training almost reached an asymptote around or before 250 epochs. However, some additional training can be seen up to xx epochs.

Figure \ref{fig:israelperformance} summarizes the performance of the three neural networks trained on the Israel templates. The performance was obtained by assuming that the most active output neuron represented the classification of the network. Inspecting the cumulative distribution of error reveals that the neural network encoding outperformed the perfect memory approach. The number of small errors was larger for the neural network than for the perfect memory. The neural network was able to classify about 70\% of templates with an error of fewer than 30 degrees in azimuth. In elevation, almost all templates were classified with an error below 15 degrees. Most (70\%) errors in location attribution were smaller than 0.5 meters. The confusion matrices confirm that most classification errors were small.

\todo[inline]{update this to reflect latest results}
Interestingly, for azimuth and elevation, classification errors were not uniform across directions. This can be seen by the classification entropy plotted in figure \ref{fig:israelperformance}. In particular, these curves show interesting peaks around zero azimuth and medium elevations. The geometry of the environment can explain these peaks. The corridor (fig. \ref{fig:datacollection}) does not return a lot of echoes from azimuths around zero. Indeed, this direction is mostly open space. The same is true for elevations above 0. Elevations around 25 return very few echoes and this serves as a reliable indicator for classifying these templates, explaining the drop in entropy for elevation = 25 degrees.

@@

Figure \ref{fig:royalperformance} shows the results for the Royal Fort Park data. These results mirror those in figure \ref{fig:israelperformance}. Again the neural network outperformed the perfect memory approach by having more smaller errors. Overall, the performance for this data set was somewhat better than for the Israel data.

\begin{figure*}
	\centering
	\includegraphics[width=1\linewidth]{../results/royal_results.pdf}
	\caption{Classification results for the Royal Fort Park site. Top row: cumulative error distributions for the azimuth, elevation and location classification. Middle row: Confusion matrices for the classifications. Bottom row: remaining classification entropy for each target (derived from the confusion matrices).}
	\label{fig:royalperformance}
\end{figure*}

@@

Figure \ref{fig:mechanism} shows the number of \pcs\ needed to capture 99\% of the templates variance. From this plot, it can be seen that the number of \pcs\ increases when shuffling the echo sequences from xx to xx. Omitting the 1 kHz filter from the  \citet{Wiegrebe2008} model increases the number of \pcs\ to xx. Including the 1 kHz filter, the average spectrum of the templates (fig. \ref{fig:mechanism}, inset) shows that most energy in the templates is contained in frequencies below 1 kHz. Therefore, if we take 1 kHz as the highest relevant frequency, it ought to be possible to completely represent templates by sampling them at 2 kSamples/sec. This corresponds to about 70 samples per template, as templates consist of 7499 samples at 219 kHz sample rate. This corresponds roughly to the number of \pcs\ required to represent templates derived from echo sequences that were shuffled  (fig. \ref{fig:mechanism}). The number of \pcs\ required to represent unshuffled templates is about half of this, i.c., \pca. Therefore, we conclude that the 1 kHz filter is the main, but not exclusive, locus of the dimensionality reduction. The structure of the echo signals also decreases the dimensionality of the templates. Therefore, we conclude that the sonar system of bats, through a number of filtering stages, compresses the 3D complexity of the world onto a lower dimensional representation.

@@

We were unable to find values for the number of neurons in the cortex of bat species. However, the mouse cortex has been estimated to contain about $9 \cdot 10^4$ neurons or $7 \cdot 10^8$ synapses per cubic millimeter \citep{Braitenberg2013}. The neural networks presented in this paper consisted of about \nneurons\ neurons and \nweights\ connections. Therefore, to the extent that the proposed neural networks can be considered as biologically plausible models of memory, they are orders of magnitude smaller than a single cubic millimeter of mouse cortex. Let alone the complete cortex, which has been estimated to contain 75 million neurons \citep{Williams2000}.

Despite their small size, the networks in this paper were able to encode (memorize) the templates at least as well as the perfect memory approach. The neural networks presented here are tiny compared to the density of cortical matter. However, the networks are also small compared to the data they encode. Table \ref{tab:sizes} lists the number of weights for the artificial neural networks and compares this number with the size of the \pca-dimensional templates. The number of floating point numbers making up the templates is larger than the number of weights by a factor of 2-3. Therefore, the networks have a smaller memory footprint than the data they encode. It should be noted that we have not made an attempt to try and to optimize (minimize) the size of the networks. From these numbers, we conclude that the low-dimensional signals provided by the bat's sonar system result in a low memory footprint and that they would use little neural resources to be stored and processed.

\begin{table}
	\centering
\begin{tabular}{lrrrrl}
	\toprule
	Site &       T &     n &      W &  W (nb\} &      R \\
	\midrule
	Israel &  206661 &  5299 &  53322 &   52425 &  25.8\% \\
	Royal &  302991 &  7769 &  51945 &   51075 &  17.1\% \\
	\bottomrule
\end{tabular}
	\label{tab:sizes}
	\caption{Table indicating the size of both template data sets and number of weights in the networks. The template size $T$ is obtained as $\pca \times n$, with $n$ the number of templates in the set. The number of weights $W$ includes all connections between neurons as well as the bias weights for each of the three networks trained. $W (nb)$ omits the bias weights. The ratio $R$ gives the ratio $W/T$.}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\bookmark}{}

\newcommand{\MinDistance}{1}
\newcommand{\MaxDistance}{7}

\newcommand{\MinDistanceFirst}{1}
\newcommand{\MaxDistanceFirst}{2}

\newcommand{\ns}{[5, 10, 20, 50, 100, 200]}
\newcommand{\nc}{[5, 10, 20, 50, 100, 200]}
\newcommand{\MinDiracs}{25}
\newcommand{\MaxDiracs}{40,000}

\newcommand{\GenerateRepeats}{10}

\newcommand{\nfilters}{8}
\newcommand{\FilterCenter}{70 kHz}

\newcommand{\CorrelationLow}{0.97}
\newcommand{\CorrelationHigh}{$>$ 0.99}

\newcommand{\pcaExplainedVar}{98\%}

\newcommand{\Epochs}{1000}

\newcommand{\FigVIIInumberII}{252}
\newcommand{\FigVIIInumberIII}{63}
\newcommand{\FigVIIInumberIIII}{296}

\newcommand{\Compression}{3-5}

%number of pca components
\newcommand{\pca}{35}
%number of neurons in models
\newcommand{\nneurons}{250 neurons (not including the input and output layers)}
%number of connections
\newcommand{\nweights}{50 thousand}

@@

Echolocating bats are long-lived, mobile animals. They use the landscape intensively for foraging, roosting, and commuting. They have excellent spatial memory \citep{Barchi2013,VonHelversen2005} and can rely on sonar to navigate to notable locations like foraging grounds and drinking places \citep[see][for references]{Vanderelst2016,Vanderelst2017}. Bats deprived of sight have been found to successfully return to their roost when displaced by up to 40 miles \citep{Stones1969,Williams1966,Davis1970,Mueller1957}. Furthermore, bats have been reported to use sonar-based recognition of landmarks, both under experimental \citep{Jensen2005,Yu2019}, and natural \citep{Verboom1999} conditions.

@@

However, it should be noted that such low dimensional descriptions have been shown to potentially contain a lot of useful information \citep{Kuc1997b,Kuc1997}. We previously demonstrated that bats might use sonar template-based scene recognition \citep{Vanderelst2016,Vanderelst2017}. Under this hypothesis, bats compare the acoustic signature of the environment to a set of previously stored signatures. We operationalized these acoustic signatures as time-intensity profiles, which could be derived directly from the cochlear output.

In this paper, we directly evaluate the hypothesis that sonar provides bats inherently with a low dimensional, yet functionally sufficient, description of the world. We test this hypothesis in two steps. In a first step, we generate an extensive collection of synthetic echo sequences. Next, we process the echo sequences using a model of the bat's auditory periphery \citep{Wiegrebe2008}. We assess the compressibility of the output of the cochlear model using \PCA. The synthetic echo sequences differ greatly in complexity. Nevertheless, the output of the cochlear model can be mapped onto a low-dimensional space. In a second step, we show that echoes collected in real bat habitats can be mapped into the same low-dimensional space, without significant loss of information. We verify this by demonstrating that the low dimensional feature space allows recognizing locations in real habitats.

@@

We created artificial echo sequences by randomly spacing ideal point reflectors. The distances of the point reflectors were selected using a two-step process. First we selected $n_{s}$ seed points $s$, uniformly distributed over a range from \MinDistance\ to \MaxDistance\ meters. Next, for every seed point $s$, we selected $n_{c}$ cloud points normally distributed around $s$, with standard deviation 0.25 m. We added a single reflector at a distance between \MinDistanceFirst\ and \MaxDistanceFirst\ to each collection of points. This two step process to modeling natural reflectors was inspired by the results of \citet{Yovel2009}, who found that echoes returning from vegetation could be better modeled using a similar two-step process than simply using uniformly spaced points. We generated \GenerateRepeats\ sets of points for each combination of $n_s \in \ns$ and $n_c \in \nc$. Synthetic echoes consisting of few reflectors are likely to consist of only weak echoes.

@@

Artificial echo sequences were filtered using a model of the bat's auditory periphery, as proposed by \citet{Wiegrebe2008}. This model simulates the temporal and spectral resolution of the bat's cochlea. The model consists of a gammatone filterbank followed by half-wave rectification and non-linear compression with an exponent of 0.4. Finally, the model includes a 1 kHz low-pass filter modeling the response characteristics of the inner hair cells. In the current implementation, we used a gammatone filterbank with \nfilters\ filters, centered around \FilterCenter. The filters were spaced to correspond to equivalent rectangular bandwidths \citep{Glasberg1990}. The output of each channel was attenuated with a time (distance) weighted factor corresponding to the atmospheric attenuation at the channel's center frequency. This operation approximated frequency-dependent atmospheric attenuation. The first 6 ms of data were removed. This was done to ensure the data corresponded with the measurement data. As indicated below, we removed the first 6 ms of the measurement  data to avoid including the pickup of the emitted signal.

Figure \ref{fig:processing}a depicts a single example of a synthetic echo sequence. It also illustrates the resulting response for each of the \nfilters\ channels of the \citet{Wiegrebe2008} model (panels b-i). From these responses, it can be seen that they are highly correlated across channels. This is confirmed when analyzing the average cross-channel correlation for all synthetic echo sequences (Fig. \ref{fig:processing}i). We calculated the correlation $\bar{\rho}$ between the output $X_i$ of each frequency channel $i$ and the mean across channels $\bar{X}$ for each synthetic echo, as follows,
%
\begin{equation}
\bar{\rho} = \frac{1}{n} \sum_i \frac{\mbox{cov}(X_i,\bar{X})}{\sigma_{X_i}, \sigma_{\bar{X}}} 
\end{equation}
%
The distribution of $\bar{\rho}$ is plotted in \ref{fig:processing}j. From this distribution, it can be seen that the value of $\bar{\rho}$ ranged from \CorrelationLow\ to \CorrelationHigh. From these high cross-channel correlations, we conclude that the output of the cochlear model can be summarized by averaging across channels without extensive loss of information.

An example of such a cross-channel sum is plotted in figure \ref{fig:processing}k. In correspondence to our previous work \citep{Vanderelst2016}, we refer to this average across frequency channels as a template.

\begin{figure*}[tb]
	\centering
	\includegraphics[width=1\linewidth]{../results/processing}
	\caption{Example of synthetic echo sequence and its processing using the \citet{Wiegrebe2008} model. (a) Example of a single synthetic echo sequence (red). The dechirped version is plotted in black. (b-i) Response of the \nfilters\ frequency channels in the \citet{Wiegrebe2008} model. From these plots, it can be seen that channels correlate highly. This is confirmed in panel j, depicting the average correlation across channels for all synthetic echo sequences analyzed. Note that the x-scale does not start at zero. (k) The output of the \citet{Wiegrebe2008} model summed across the frequency channels, is referred to as a template in this paper. Panel (l) shows the cumulative proportion of explained variance as a function of number of \pc\ across all templates for all synthetic echo sequences.}
	\label{fig:processing}
\end{figure*}

We used principal components analysis (\PCA\ ) to assess the dimensionality of the templates generated from the synthetic echo sequences. We found that almost all of the variance ($> 99\%$) in the templates could be captured by \pca\ components (see figure \ref{fig:processing}l). Some examples of templates reconstructed from the principal components are shown in figure \ref{fig:synthetictemplates}).

\begin{figure*}[tb]
	\centering
	\includegraphics[width=1\linewidth]{../results/synthetic_templates}
	\caption{Example of synthetic dechirped echo sequences, their corresponding templates and the templates reconstructed from the \pca\ \pcs. (a-c) Three examples of synthetic echo sequence waveforms. Panels (d-f) depict the resulting templates (i.e., summation across the output channels of the \citet{Wiegrebe2008} model). These panels also show the result of projecting the templates into a \pca D \pc\ space and transforming the result back to the original coordinates.}
	\label{fig:synthetictemplates}
\end{figure*}

In this section, we  used a generative model for naturalistic echoes. We assumed that echoes sequences received by bats can be considered as generated by anisotropically distributed point reflectors. Using this model, we have derived a low dimensional space ($D = \pca$), which can be used to describe the templates resulting from the artificial echo sequences. This implies that, after filtering through (a model of) the bat's auditory system, these artificial echoes can be converted into low dimensional descriptions. The original echo sequences, generated by \MinDiracs\ to \MaxDiracs\ point reflectors effectively map to a \pca\ dimensional vector. In the remainder of the paper, we will assess whether this low dimensional space allows describing the echoes from real bat habitats as collected using an ensonification device.

@@

We should point out that we did not take any steps to avoid so-called overfitting by the neural networks. Overfitting occurs when a neural network \citep{Ghotra2017}, or other mathematical models \citep{Hawkins2004}, extract complicated relationships between inputs and outputs that do not hold beyond the training examples. Overfitting typically reduces the ability of the model to generalize its predictive power to new data. However, in this case, the model is not required to generalize to other environments. Instead, we are only interested in whether the neural networks can learn and classify the set of training examples. Nevertheless, it would be beneficial if the neural networks would be capable of classifying templates corresponding to directions that are slightly different than those included in the data sets. Indeed, this is a feature of the Euclidean distance measure used in implementing the perfect memory. In that approach, novel templates will be classified to positions with similar templates. We verified whether this properties was also found in the neural networks the case by generating a set of templates by interpolating in azimuth and elevation between the directions ensonified in the data set. In our data sets, we ensonified 31 different azimuth directions and 7 elevation directions. The interpolated data consisted of 30 azimuths and 7 elevations. We used the neural networks trained on the original data to classify these interpolated data.

@@

We found that the templates derived from acoustic data collected in real habitats could be well represented by the \pca\ components derived from synthetic data. This \pca-dimensional space could represent \pcaExplainedVar\ of the variance in the templates. Figure \ref{fig:empiricaltemplates} shows examples of templates and their reconstructed counterparts. Therefore, although the model used to generate echo sequences was very simple, these results indicate that the \pca D feature space derived from the generative echo model could adequately represent templates resulting from real acoustic data.

@@

Figure \ref{fig:history} depicts the training history of all networks. This figure shows that, in all cases, training almost reached an asymptote around or before 250 epochs. However, some additional training can be seen up to \Epochs\ epochs (when learning was arbitrarily halted).

%%
%xx THIS PARAGRAPH TAKES NUMBERS FROM FIG 6
%%

Figure \ref{fig:israelperformance} summarizes the performance of the three neural networks trained on the Israel templates. The performance was obtained by assuming that the most active output neuron represented the classification of the network. Inspecting the cumulative distribution of error reveals that the neural network encoding performed as least as well as the perfect memory approach. The number of small errors was larger for the neural network than for the perfect memory. The neural network was able to classify about 80\% of templates with an error of fewer than 30 degrees in azimuth. In elevation, almost all templates were classified with an error below 15 degrees. Most (78\%) errors in location attribution were smaller than 0.5 meters. The confusion matrices confirm that most classification errors were small.

Interestingly, for azimuth and elevation, classification errors were not uniform across directions. This can be seen by the classification entropy plotted in figure \ref{fig:israelperformance}. In particular, these curves show  peaks around zero azimuth and medium elevations. The geometry of the environment can explain these peaks. The corridor (fig. \ref{fig:datacollection}) does not return a lot of echoes from azimuths around zero. Indeed, this direction is mostly open space. The same is true for elevations above 0.

@@

%%
%xx THIS PARAGRAPH TAKES NUMBERS FROM FIG 7
%%

Figure \ref{fig:royalperformance} shows the results for the Royal Fort Park data. These results mirror those in figure \ref{fig:israelperformance}. Again the neural network performed at least as good as the perfect memory approach. For azimuth, the perfect memory approach slightly outperform the neural network (notice that y-scale in the top panels of this figure differ from figure \ref{fig:israelperformance}). Overall, the performance for this data set was better than for the Israel data. This is probably due to the fact that echoes were collected closer to reflectors (vegetation) than in the Israel data set, which leads to strong echoes.

\begin{figure*}
	\centering
	\includegraphics[width=1\linewidth]{../results/royal_results.pdf}
	\caption{Classification results for the Royal Fort Park site. Top row: cumulative error distributions for the azimuth, elevation and location classification (Notice the different y-scale for these plots than in figure \ref{fig:israelperformance}). Middle row: Confusion matrices for the classifications. Bottom row: remaining classification entropy for each target (derived from the confusion matrices).}
	\label{fig:royalperformance}
\end{figure*}

@@

Figure \ref{fig:mechanism} shows the number of \pcs\ needed to capture 99\% of the templates variance. From this plot, it can be seen that the number of \pcs\ increases when shuffling the echo sequences from \pca\ to \FigVIIInumberIII\. Omitting the 1 kHz filter from the  \citet{Wiegrebe2008} model increases the number of \pcs\ to \FigVIIInumberII. Including the 1 kHz filter, the average spectrum of the templates (fig. \ref{fig:mechanism}, inset) shows that most energy in the templates is contained in frequencies below 1 kHz. Therefore, if we take 1 kHz as the highest relevant frequency, it ought to be possible to completely represent templates by sampling them at 2 kSamples/sec. This corresponds to about 70 samples per template, as templates consist of 7499 samples at 219 kHz sample rate. This corresponds roughly to the number of \pcs\ required to represent templates derived from echo sequences that were shuffled  (fig. \ref{fig:mechanism}). The number of \pcs\ required to represent unshuffled templates is about half of this, i.c., \pca. Therefore, we conclude that the 1 kHz filter is the main, but not exclusive, locus of the dimensionality reduction. The structure of the echo signals also decreases the dimensionality of the templates. The sonar system of bats, through a number of filtering stages, compresses the 3D complexity of the world onto a lower dimensional representation.

@@

We were unable to find values for the number of neurons in the cortex of bat species. However, the mouse cortex has been estimated to contain about $9 \cdot 10^4$ neurons or $7 \cdot 10^8$ synapses per cubic millimeter \citep{Braitenberg2013}. The neural networks presented in this paper consisted of \nneurons\ and \nweights\ connections. Therefore, to the extent that the proposed neural networks can be considered as biologically plausible models of memory, they are orders of magnitude smaller than a single cubic millimeter of mouse cortex. Let alone the complete cortex, which has been estimated to contain 75 million neurons \citep{Williams2000}.

Despite their small size, the networks in this paper were able to encode (memorize) the templates at least as well as the perfect memory approach. The neural networks presented here are tiny compared to the density of cortical matter. However, the networks are also small compared to the data they encode. Table \ref{tab:sizes} lists the number of weights for the artificial neural networks and compares this number with the size of the \pca-dimensional templates. The number of floating point numbers making up the templates is larger than the number of weights by a factor of \Compression. Therefore, the networks have a smaller memory footprint than the data they encode. It should be noted that we have not made an attempt to try and to optimize (minimize) the size of the networks. From these numbers, we conclude that the low-dimensional signals provided by the bat's sonar system result in a low memory footprint and that they would use little neural resources to be stored and processed.

\begin{table}
	\centering
\begin{tabular}{lrrrrl}
	\toprule
	Site &       T &     n &      W &  W (nb) &      R \\
	\midrule
	Israel &  183430 &  5395 &  52875 &   51975 &  28.8\% \\
	Royal &  264146 &  7769 &  51345 &   50475 &  19.4\% \\
	\bottomrule
\end{tabular}
	\label{tab:sizes}
	\caption{Table indicating the size of both template data sets and number of weights in the networks. The template size $T$ is obtained as $\pca \times n$, with $n$ the number of templates in the set. The number of weights $W$ includes all connections between neurons as well as the bias weights for each of the three networks trained. $W (nb)$ omits the bias weights. The ratio $R$ gives the ratio $W/T$.}
\end{table}
